Differential Testing Runtime Engines--Lessons Learned from the JavaScript Domain

### 2018-07-11 paper/paper.tex
minor changes in infra

\section{ES6 design}
\Fix{to appear}

@@

Figure~\ref{fig:workflow} illustrates the infrastructure we used in
this study.
The bug-finding process
takes on input JS files from regression test suites of various JS
engines and generates warnings on output. Boxes in the figure denote encapsulation;
arrowed lines indicate control flow (dashed) and data flow
(filled). The cycle icons denote repetition--the leftmost icon
indicates that each file in the input list will be analyzed in
separate whereas the rightmost icon shows that a single file will be
fuzzed multiple times. The bug-finding process works as follows.  Considering the case
where fuzzing is not selected, as illustrated in the inner box at the bottom
of the figure, the oracle checks whether or not the output produced
for that file is consistent across all engine implementations. In case
the test passes in all engines or fails in all engines (\ie{}, the
output is consistent), the infrastructure discards the test. Otherwise, it considers the input as potentially
fault-revealing; hence interesting for human inspection. Considering
the case where fuzzing~\cite{fuzz-testing-history} is selected, new
inputs are obtained from a given input using some off-the-shelf
fuzzer. Several fuzzing methods have been proposed in the
  past, varying with respect to how new inputs are generated (\eg{},
  coverage-based~\cite{afl,honggfuzz},
  grammar-based~\cite{grammarinator,jsfunfuzz}, and
  random-based~\cite{radamsa}). Section~\ref{sec:objects:fuzzers} describes the
  fuzzers we selected. The workflow of the infrastructure with fuzzing
  enabled is similar to that of no fuzzing. In this case, however, multiple warnings can be produced
for a given seed input.

The infrastructure outputs a list of warnings for human inspection.
To reduce the number of false alarms, we clustered warnings in two
groups, reflecting their likelihood to manifest a real bug. Warnings
in the HI group are associated with the cases when the anomaly has been
detected during the execution of the test code or its close neighborhood\Comment{ as
  opposed to that of some internal JS function}, crashes (ie. FatalError) and core dumps 
  are considered HI group as well. The rationale is that
the test in this group executed without violating any internal checks
of the API. In constrast, warnings in the LO group reflect the cases where the
anomaly was observed during the execution of functions from standard JS
libraries.\Mar{what is that exactly? can we cite? is that only spec or
actually code as most of java.* libraries.}We
found that different engines often check pre-conditions of those
functions differently. It can happen, for example, that one engine
enforces a weaker pre-condition compared to another.
% \Mar{why is that?
% that should not happen if the spec was fully documented and engines
% properly implemented those checks. Explain and give example.}
\Igor{these cases happen because the specification describes how a function
should work, however the internal implementation is defined by the
engine developers}\Mar{If you confirm that there is no code in specs
  (see comment above), what would be those abstract
  functions/interfaces that you mentioned to me the other day?}.
In those cases,
our infrastructure would observe a discrepancy that is more likely to
be associated with a bug in the (fuzzed) test; not the code. Although
we did find real bugs from warnings in the LO group, the proportion
was much lower compared to the HI group--only 12\% of the reals bugs
we found originated from the LO category. \Mar{show real examples of
  HI and LO. Use the stacktraces to explain what is going on.}

% no-bug low console output

% bug high console output

@@

@@

An example of a warning from the HI group is defined in Figure~\ref{fig:hi-priority}. 
This is a testcase from WebKit.es6 suite that it was mutate by radamsa fuzzer, the 
initial seed has in line 3 the code \CodeIn{"foo".repeat(3)} but the fuzzer changed the 
integer 3 to a big integer number. We reported this case in chakra due a core dumps that occurs
during the runtime, however this case was rejected due \CodeIn{incompatibility by design} that
this is an intentional behavior of engine that crash the process if it runs out of memory
\cite{bug4979}.

>>>>

@@

Figure~\ref{fig:workflow} illustrates the infrastructure we used in
this study.
The bug-finding process
takes on input JS files from regression test suites of various JS
engines and generates warnings on output. Boxes in the figure denote encapsulation;
arrowed lines indicate control flow (dashed) and data flow
(filled). The cycle icons denote repetition--the leftmost icon
indicates that each file in the input list will be analyzed in
separate whereas the rightmost icon shows that a single file will be
fuzzed multiple times. The bug-finding process works as follows.  Considering the case
where fuzzing is not selected, as illustrated in the inner box at the bottom
of the figure, the oracle checks whether or not the output produced
for that file is consistent across all engine implementations. In case
the test passes in all engines or fails in all engines (\ie{}, the
output is consistent), the infrastructure discards the corresponding
input. Otherwise, it considers the input as potentially
fault-revealing; hence interesting for human inspection. Considering
the case where fuzzing~\cite{fuzz-testing-history} is selected, new
inputs are obtained from a given input using some off-the-shelf
fuzzer. Several fuzzing methods have been proposed in the
  past, varying with respect to how new inputs are generated (\eg{},
  coverage-based~\cite{afl,honggfuzz},
  grammar-based~\cite{grammarinator,jsfunfuzz}, and
  random-based~\cite{radamsa}). Section~\ref{sec:objects:fuzzers} describes the
  fuzzers we selected. The workflow of the infrastructure with fuzzing
  enabled is similar to that of no fuzzing. In this case, however, multiple warnings can be produced
for a given seed input.

The infrastructure outputs a list of warnings for human inspection.
To reduce the number of false alarms, we clustered warnings in two
groups, reflecting their likelihood to manifest a real bug. Warnings
in the HI group are associated with the cases when the anomaly has been
detected during the execution of the test code or its close neighborhood\Comment{ as
  opposed to that of some internal JS function}, crashes (ie. FatalError) and core dumps 
  are considered HI group as well. The rationale is that
the test in this group executed without violating any internal checks
of the API. In constrast, warnings in the LO group reflect the cases where the
anomaly was observed during the execution of some standard JS
function. In addiction, we observed that several testcases run loops that can 
affect the time-consuming of an execution, we decided to use an watcher to check 
if an test consumes more than 5 seconds to run, if exceed this condition we stop 
the engine execution and considered these cases as TIMEOUT error. These tests are 
labeled as LO group.
\Mar{is this correct? what are those?}We
found that different engines often check the pre-conditions of those
functions differently. It can happen, for example, that one engine
enforces a pre-condition that another engine does not, 
% \Mar{why is that?
% that should not happen if the spec was fully documented and engines
% properly implemented those checks. Explain and give example.}
\Igor{these cases happen because the specification describes how a function
should work, however the internal implementation is defined by the engine developers}.
In those cases,
our infrastructure would observe a discrepancy that is more likely to
be associated with a bug in the (fuzzed) test; not the code. Although
we did find real bugs from warnings in the LO group, the proportion
was much lower compared to the HI group--only 12\% of the reals bugs
we found originated from the LO category. \Mar{show real examples of
  HI and LO.}

\Igor{
  We defined if an warning is in HI or LO group according to console output.
  The error stream in the output shows relevant informations that we can 
  process. The Figure~\ref{fig:hi-priority} shows an example of a warning 
  considered as a HI group, the stream output came from V8 engine. The error message 
  shows informations related to the assertion code (see at line 2) 
  that thows an Error exception. This case was considered as HI groups and after 
  several discussion and specification analysis we reported as a true positive example (see \cite{bug4978}).
}

% bug high console output
This a case of a warning reported as HI priority, the Figure~\ref{} shows
the output console of V8 engine. We consider this case as a HI group due 
the fail by assertion, defined at line 2 as \CodeIn{throw new Error("Test failed");}

\begin{figure}[h!]
  \centering
  \scriptsize
  \lstset{escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c,
    numberstyle=\tiny,
    morekeywords={assertEq, var, yield, in, function, 
    typeof, return, throw, new, Error, if},
  }
  \begin{lstlisting}
seeds/Duktape/ecma_fixed/test-dev-bound-func-many-args.js:4: Error: Test Failed
throw new Error("Test Failed");
  ^
Error: Test Failed
  at String.target (seeds/Duktape/ecma_fixed/test-dev-bound-func-many-args.js:4:13)
  at seeds/Duktape/ecma_fixed/test-dev-bound-func-many-args.js:23:1
\end{lstlisting}
\normalsize
\caption{Warning captured as HI priority.}
\label{fig:hi-priority}
\end{figure}

\begin{figure}[h!]
  \centering
\begin{minipage}{.45\textwidth}
  \scriptsize
  \lstset{escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c,
    numberstyle=\tiny,
    morekeywords={assertEq, var, yield, in, function, 
    typeof, return, throw, new, Error, if},
  }
  \begin{lstlisting}[caption=JavaScript code fuzzed by radamsa,frame=tlrb]{Name}
  void code()
  {

  }
  \end{lstlisting}
  \end{minipage}\vfill
  \begin{minipage}{.45\textwidth}
    \scriptsize
    \lstset{escapeinside={@}{@},
      numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
      basicstyle=\ttfamily\scriptsize, boxpos=c,
      numberstyle=\tiny,
      morekeywords={assertEq, var, yield, in, function, 
      typeof, return, throw, new, Error, if},
    }
  \begin{lstlisting}[caption=Console Output,frame=tlrb]{Name}
  void code()
  {

  }
  \end{lstlisting}
  \end{minipage}
  \caption{Warning captured as HI priority.}
  \label{fig:lo-priority}
\end{figure}

% no-bug low console output
\begin{figure}[h!]
  \centering
  \scriptsize
  \lstset{escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c,
    numberstyle=\tiny,
    morekeywords={assertEq, var, yield, in, function, 
    typeof, return, throw, new, Error, if},
  }
  \begin{lstlisting}
\end{lstlisting}
\normalsize
\caption{Warning captured as HI priority.}
\label{fig:lo-priority}
\end{figure}

@@

\subsection{ES6 design}
\Fix{to appear}

@@

An example of a warning from the HI group is defined in Figure~\ref{fig:hi-priority}. 
This is a testcase from WebKit.es6 suite that it was mutate by radamsa fuzzer, the 
initial seed has in line 3 the code \CodeIn{"foo".repeat(3)} but the fuzzer changed the 
integer 3 to a big integer number. We reported this case in chakra due a core dumps that occurs
during the runtime, however this case was rejected due \CodeIn{incompatibility by design} that
this is an intentional behavior of engine that crash the process if it runs out of memory.
